PANCHANGE_analysis

### 2020-12-09 PANCHANGE_analysis.Rmd
added figure path, folder and gitignore

@@

# R functions
## Half-violin plot
```{r Half-violin plot}
source("https://raw.githubusercontent.com/datavizpyr/data/master/half_flat_violinplot.R")
```

@@

# get lm object to do forest plots

gad_prepan_model1b_lm <- model1b.lm(outcome = "gad.diff_score_base_prepan",
                                           data_set = "dat.prepan")

@@

# function for formula
model1b.lm.form <- function(outcome,explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")

  # assign it globally with the right variable name.
  assign(paste0(outcome,explan_var,".glmformula"),
         glm.formula,
         envir = .GlobalEnv
  )

@@

@@

  ## Disoprder dimension  
  groups <- c(group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group)

@@

  # assign dataframe to global environment
  assign(dfname, df, envir = .GlobalEnv)

@@

```{r generate datasets for all plots}
# prepandemic and retrospective, grouped by disorder measure
lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","GAD-7", "gad.prepan.lm.for.plot")
lmoutput_format(gad.retro.lm,"gad.sum_score_retro","GAD-7", "gad.retro.lm.for.plot")

@@

@@

@@

```
### time point 
```{r forest plot by time point gad, fig.height=14, fig.width=8}

@@

```
```{r forest plot by time point phq, fig.height=14, fig.width=8}

@@

```
```{r forest plot by time point pcl, fig.height=14, fig.width=8}

@@

```
```{r forest plot by sample retro only phq, fig.height=14, fig.width=8}

@@

```
```{r forest plot by sample retro only pcl, fig.height=14, fig.width=8}

>>>>

opt_chunk$set(fig.path="./figures")

@@

# R functions

## Half-violin plot
```{r Half-violin plot}
source("https://raw.githubusercontent.com/datavizpyr/data/master/half_flat_violinplot.R")
```

@@

@@

model1b.lm.form <- function(outcome, explan_var, data_set) {

  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")

  # assign it globally with the right variable name.
  assign(paste0(outcome,".", explan_var, ".glmformula"),
         glm.formula,
         envir = .GlobalEnv

  )
}

@@

### add a single "other ethnicity individual" as a jitter for NBR so this category remains included wihout adding explanation.
```{r add jitter "other" for NBR other ethnicity so this cat is available for plotting}

dat.retro.nbr$Ethnicity_collapsed[801] <- "Other"  #this person was an NA
dat.retro.nbr$Ethnicity_collapsed[998] <- "Other"  #this person was an NA

@@

  ## Disorder dimension  
  groups <- c(group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group)

@@

  # assign dataframe to global environment
  assign(dfname, df, envir = knitr::knit_global())

@@

```{r generate datasets for all plots}

# prepandemic and retrospective, grouped by disorder measure
lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","GAD-7", "gad.prepan.lm.for.plot")
lmoutput_format(gad.retro.lm,"gad.sum_score_retro","GAD-7", "gad.retro.lm.for.plot")

@@

# prepandemic and retrospective, grouped by time point
lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","Prepandemic", "gad.prepan.lm.for.plot.timegroup")
lmoutput_format(gad.retro.lm,"gad.sum_score_retro","Retrospective", "gad.retro.lm.for.plot.timegroup")

lmoutput_format(phq.prepan.lm,"phq.sum_score_prepan","Prepandemic", "phq.prepan.lm.for.plot.timegroup")
lmoutput_format(phq.retro.lm,"phq.sum_score_retro","Retrospective", "phq.retro.lm.for.plot.timegroup")

lmoutput_format(pcl.prepan.lm,"pcl.sum_score_prepan","Prepandemic", "pcl.prepan.lm.for.plot.timegroup")
lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","Retrospective", "pcl.retro.lm.for.plot.timegroup")

@@

# Disorder groups: No PCL

plot.dat.disorder.prepan.gadphq <- rbind(gad.prepan.lm.for.plot,
                                  phq.prepan.lm.for.plot)

plot.dat.disorder.retro.gadphq <- rbind(gad.retro.lm.for.plot,
                                 phq.retro.lm.for.plot)

@@

### disorder (no PCL)
```{r forest plot by disorder prepan, fig.height=14, fig.width=8}

lm.forest(plot.dat.disorder.prepan.gadphq,"Predictors of pandemic symptoms controlling for prepandemic symptoms")

lm.forest(plot.dat.disorder.retro.gadphq,"Predictors of pandemic symptoms controlling for retrospective symptoms")

### time point 
```{r forest plot by time point gad, fig.height=14, fig.width=8}

@@

```{r forest plot by time point phq, fig.height=14, fig.width=8}

@@

```{r forest plot by time point pcl, fig.height=14, fig.width=8}

@@

```{r forest plot by sample retro only phq, fig.height=14, fig.width=8}

@@

```{r forest plot by sample retro only pcl, fig.height=14, fig.width=8}
